\documentclass[10pt,letterpaper]{article}
\input{../common/include}

% Custom definitions
\newcommand{\doctitle}{List of Deliverables}
\newcommand{\docsubtitle}{\input{../common/title}}

\input{../common/aliases}
\renewcommand{\revisionnum}{1.3}
\input{../common/urlsetup}
\input{../common/pagesetup}
\input{../common/titlepage}

% Begin Document
\begin{document}
\input{../common/presections}
\section{About This Document}
This document outlines the full list of deliverables presented to the client at the end of the project (in addition to how they are to be delivered).

\section{List of Deliverables}
\label{list}
\subsection{Hardware Artifacts}
\subsubsection{Computing Platform Artifacts}
\begin{itemize}
\item 1 -- Raspberry Pi 4
\item 1 -- Micro-SD Card (for Raspberry Pi)
\item 1 -- Raspberry Pi Camera Module (5 MP)
\item 1 -- USB-C to Mains Adapter
\item 1 -- Ethernet Cord (10 ft)
\item 1 -- Zedboard
\item 1 -- SD Card (for Zedboard)
\item 1 -- 12V Barrel Plug to Mains Adapter
\item 2 -- Micro-USB to USB-A Cable
\end{itemize}

\subsubsection{Multirotor Artifacts}

The following list of items are already assembled into a single entity upon delivery. 

\begin{itemize}
\item 1 -- JMT 560 mm Carbon Fibre Frame
\item 1 -- ArduPilotMega Autopilot Flight Controller with GPS and Barometer sensors
\item 1 -- RadioLink Receiver
\item 4 -- Unnamed 3508 700 kV Brushless DC Motor
\item 4 -- HobbyZone 40.0 A Electric Speed Controller
\item Custom-Made Mechanical Parts (see CAD drawings document)
\end{itemize}

The following list of accessories are essential to configure the multirotor for flight.

\begin{itemize}
\item 1 -- 3S 5000 mAh Lithium Polymer Battery with XT-60 Connector
\item 1 -- AC to DC 3S Battery Charger
\item 1 -- RadioLink Transmiter
\item 8 -- AA Alkaline Batteries for the Transmitter
\end{itemize}


\subsection[Document Artifacts]{Document Artifacts\footnote{All referenced documents can be found at \url{https://github.com/Capstone-Skynet/Capstone-Skynet.github.io}}}

\begin{itemize}
\item Requirements Specification
\item Design Specification
\item CAD Drawings
\item Validation Specification and Results
\item Operations, Maintenance, and Upgrades Specifications
\item List of Deliverables
\end{itemize}

\subsection{Other Artifacts}
\begin{itemize}
\item Demonstrative Video
\item Oral Presentation
\item Project Repositories
\begin{itemize}
    \item Documents and Meeting Notes Repository ({\url{https://github.com/Capstone-Skynet/Capstone-Skynet.github.io}})
    \item Source Code Repository ({\url{https://github.com/Capstone-Skynet/Integration}})
    \item CAD models of hardware and mechanical components
\end{itemize}
\end{itemize}

\section{Equipment Delivery}
To conform with the physical distancing requirements imposed in light of the COVID-19 pandemic, the delivery of equipment listed in Section \ref{list} to Dr. Lis will be delayed until Summer 2020. 

If physical distancing measures are relaxed prior to September 1st, 2020, Peter Deutsch (me@peterdeutsch.ca) will hand-deliver the components to Dr. Lis (mieszko@ece.ubc.ca) at an agreed upon date. Otherwise, he will deposit the items in a secure location (Kaiser Building Room 4025) for the client to pick up at a later time. 

The estimated value of the equipment being delivered is \$1100.

% Appendix (uncomment to enable appendix)
% \clearpage
% \appendix
% \section{Appendix name}\label{appendix:sample-appendix}
% Content here

\end{document}
