This project concludes on \textbf{April 3rd, 2020}, at which point the client
and the instructors will receive the following project deliverables:

\subsubsection{Hardware Artifacts}

\begin{enumerate}

\item \textbf{Drone Prototype}:
A fully integrated FPGA computing platform mounted on a remote-controlled
drone that can capture video using an on-board camera.
The computing platform utilizes FPGA-based neural network accelerators to 
process the video data and detect and track one or more designated objects.
The platform transmits video data and associated machine learning metadata
to a ground station.

\item \textbf{Ground Station Prototype}:
A system that receives wireless video data and machine learning metadata from
the drone and displays both on-screen. The ground station also logs the received data 
to files for further research and analysis purposes.

\end{enumerate}

\subsubsection{Document Artifacts}\label{document-artifacts}

\begin{enumerate}

\item\textbf{Requirements Specification}:
A document outlining the functional and non-functional requirements
of the prototypes.

\item \textbf{Design Specification}:
A document describing the high-level architecture and design of technical subsystems.

\item \textbf{Validation Specification and Results}:
A document describing system testbenches, validation techniques, and validation/testing results.

\item \textbf{Operations, Maintenance, and Upgrades Specifications}:
A document, similar to a operation manual, outlining installation instructions,
recommended maintenance, and common troubleshooting guides.

\item \textbf{List of Deliverables}

\end{enumerate}

\subsubsection{Other Artifacts}

\begin{enumerate}

\item \textbf{Demonstrative Video}
\item \textbf{Oral Presentation and Poster}
\item \textbf{Project Repositories}: Repositories that include all source code,
generated netlists, CAD designs, spreadsheets, and other documents.

\end{enumerate}