\subsubsection{Risk Management}
The student team has generated a list of potential risks which threaten the viability of the project and have assigned a likelihood and impact value to each of them (Table \ref{riskprofile}). The \textit{risk index} for each risk is the product of these two values: \textit{likelihood} and \textit{impact}.

\textit{To mitigate the outlined risks, the following risk management protocol is followed:}


If the risk index is \textbf{greater or equal to 0.4}, then the risk mitigation protocol \textit{must} be followed. This entails creating a card for the specific risk on Trello (the team's project management tool), discussing the status of the risk during the weekly group meeting, and providing immediate updates to the status of the risk on Slack as they occur.

If the risk index is \textbf{less than 0.4}, then the above risk mitigation protocol \textit{may} be followed, if deemed necessary. Otherwise, the risk is simply monitored for updates.

The risk profile is updated/reviewed weekly (during the team meeting) and as otherwise necessary. 


\subsubsection{Potential Risks}

\begin{center}

% Make the table more stretched out
\renewcommand{\arraystretch}{1.3} % Default value: 1

\begin{longtable}{p{0.6\linewidth} *{3}{r}}

\caption{A risk profile table outlining the a list of potential risks.}\\
\hline
\textbf{Risk description} & \textbf{Likelihood} & \textbf{Impact} & \textbf{Risk ($\downarrow$)} \\
\hline
\endfirsthead

\multicolumn{4}{c}%
{\tablename\ \thetable\ -- \textit{Continued from previous page}} \\
\hline
\textbf{Risk description} & \textbf{Likelihood} & \textbf{Impact} & \textbf{Risk ($\downarrow$)} \\
\hline
\endhead

\hline \multicolumn{4}{r}{\textit{Continued on next page}} \\
\endfoot

\hline
\endlastfoot

Drone flight hardware (flight controllers, radio, motors) cannot function due to crashes and/or damage. & 0.9 & 1.0 & 0.90 \\ \hline
Payload is too heavy which significantly increases drone motor requirements and significant reduction in flight duration. & 0.8 & 0.8 & 0.64 \\ \hline
Accidents that damage the drone and computating equipment that require extra budget that we may not have. & 0.6 & 0.9 & 0.54\\ \hline
Loss of drone hardware and payload during flight and cannot be recovered (total loss). & 0.5 & 1.0 & 0.50 \\\hline
Not enough time commitment from team members. & 0.7 & 0.7 & 0.49\\ \hline
Access to tools and shops for modifiying and repairing drone hardware is inadequate or non-existent. & 0.6 & 0.8 & 0.48\\ \hline
Underestimation of project scope or work required, leading to insufficient time managemnet and burn-outs. & 0.5 & 0.9 & 0.45\\ \hline
Payload is too heavy which exceeds total take-off weight. & 0.4 & 1.0 & 0.40 \\ \hline
Legacy documents for the project are insufficient, resulting in poor maintainability/extensibility for the client. & 0.7 & 0.5 & 0.35\\ \hline
Financial inefficiencies leading to overbudget or lack of capital. & 0.4 & 0.8 & 0.32\\ \hline
Constrained to purchase lower-quality components due to budget and results in lower performance. & 0.6 & 0.5 & 0.30 \\ \hline
Team is indecisive or team leader cannot make a timely decision --- results in delay. & 0.4 & 0.6 & 0.30\\ \hline
Development and managment technique and methodology is not effective, leading to productivity losses. & 0.4 & 0.7 & 0.28\\ \hline
Not enough time to work on documentation. & 0.7 & 0.4 & 0.28\\ \hline
Scope of the project is overestimated which leads to diversification of vision of the project. & 0.5 & 0.5 & 0.25\\ \hline
Not enough machine learning training data. & 0.5 & 0.5 & 0.25\\ \hline
Not enough FPGA logic elements to implement a desired ML model. & 0.5 & 0.5 & 0.25\\ \hline
Failure to acquire regulatory compliance resulting in inability fly drone legally. & 0.3 & 0.7 & 0.21\\ \hline
The software, tools or development environment for the project is inadequate. & 0.4 & 0.5 & 0.20\\ \hline
Knowledge and skill regarding ML is insufficient. & 0.5 & 0.4 & 0.20 \\ \hline
Technical debt paydown impact project timeline. & 0.4 & 0.5 & 0.20\\ \hline
Deliverables and objectives failing to meeting client’s expectations. & 0.2 & 0.9 & 0.18 \\ \hline
Client demands modification to the scope and requirements of the project that leads to delays or feature cuts. & 0.3 & 0.6 & 0.18\\ \hline
Team lacking in effective communication which leads to overlapping work, missed work, and incompatible work. & 0.4 & 0.4 & 0.16\\ \hline
Internal documentation or documentation for libraries and parts are not sufficient for development. & 0.4 & 0.4 & 0.16\\ \hline
Camera module lacking in documentation. & 0.2 & 0.8 & 0.16\\ \hline
New technology or research that changes the scope significantly. & 0.2 & 0.5 & 0.10\\ \hline
Sabotage of the project. & 0.1 & 1 & 0.10\\ \hline
Sudden loss of client. & $\leq$0.1 & 1 & 0.10\\ \hline
Sudden loss of team member. & $\leq$0.1 & 0.9 & 0.09\\ \hline
FPGA board lacks documentation. & $\leq$0.1 & 0.8 & 0.08\\ \hline
Client is not cooperative or does not provide necessary information. & $\leq$0.1 & 0.8 & 0.08\\ \hline
Key components are not available or takes too long to deliver. & 0.1 & 0.7 & 0.07\\ \hline
Purchased orders of equipment or tools delayed or lost. & 0.1 & 0.5 & 0.05\\ \hline
Client is not available enough to provide significant help. & $\leq$0.1 & 0.5 & 0.05\\ \hline
Lacking resources in machine learning knowledge. & $\leq$0.1 & 0.5 & 0.05\\ \hline
Camera module fails to interface with FPGA. & $\leq$0.1 & 0.5 & 0.05\\ \hline
Data transmitter fail to interface with FPGA. & $\leq$0.1 & 0.5 & 0.05\\ \hline
Market competition significantly affects project requirements and scope. & $\leq$0.1 & 0.4 & 0.04\\ \hline
Software license does not allow our application to be delivered. & 0.1 & 0.3 & 0.03\\ \hline
Laws regarding drone operation and piloting change significantly. & 0.1 & 0.2 & 0.02\\ \hline
\label{riskprofile}
\end{longtable}
\end{center}
