\paragraph{\underline{T.ACP.1: Wireless Connection Checking}}

This test is performed automatically after system boot to confirm that the wireless connection between the PMB and the ground station has been established.

\textbf{Addresses}: F.CM.1, F.CM.2, F.BS.3, F.BS.5

\textbf{Procedure}:
\begin{enumerate}[noitemsep]
    \item The platform management board boots up and connects to the base station.
    \item The base station accepts and establishes the connection.
\end{enumerate}

\textbf{Verification}: 
Upon successful completion, the base station displays a new connection message in its log field.

\paragraph{\underline{T.ACP.2: Hardware Accelerator Initialization Check}}

This test is performed automatically after system boot to confirm that the hardware acceleration core has booted and that the HPS can interface with it successfully.

\textbf{Addresses}: NF.CP.1, F.ML.1, F.ML.2, F.ML.4

\textbf{Procedure}:
\begin{enumerate}[noitemsep]
	\item Reference ML results are generated using a sample image during system development, with the results being stored in non-volatile memory.
    \item On boot, the platform management board sends an identical sample frame to the hardware acceleration core.
    \item The hardware acceleration core processes the frame and returns the ML results to the PMB.
    \item The platform management board compares the newly generated results to the reference results, and returns test results to the base-station.
\end{enumerate}

\textbf{Verification}: 
The test fails if no results are returned from the HW core, or if the generated results do not match the expected (reference) results.