\paragraph{\underline{T.G.1: System Boot Test}}

This test verifies the system can boot to an operational/ready stage.

\textbf{Addresses}: NF.CP.2, F.CP.2

\textbf{Procedure}:
\begin{enumerate}[noitemsep]
    \item Ensure power is applied to the system.
    \item Press the power button.
    \item Connect the base station to the server.
    \item Wait for the confirmation to show up on the base station.
\end{enumerate}

\textbf{Verification}: 
If a warning/error message is displayed, or no message is received on the base station after 2 minutes, the test has failed. Otherwise, the test passes.

%

\paragraph{\underline{T.G.2: System Logging Test}}

This test triggers a system fault, verifying an appropriate error message is displayed and the event is appropriately logged.

\textbf{Addresses}: F.CP.4, F.BS.5

\textbf{Procedure}:
\begin{enumerate}[noitemsep]
    \item Turn off the Wi-Fi router that the platform management board is configured to connect to.
    \item Boot the system.
    \item Let the system run for 5 minutes.
    \item Verify that the failed connection attempts are logged at both the base station and the PMB.
\end{enumerate}

\textbf{Verification}: 
An error message must appear at the base station. The log files on both the PMB and base station should clearly indicate that the system couldn't connect to the router and attempted to reconnect. If the error message is correctly displayed and the logs is correctly generated, this test passes.

%

\paragraph{\underline{T.G.3: Wireless Connection Test}}

This test verifies the effective range of the wireless connection between the PMB and the base station.

\textbf{Addresses}: F.BS.3, NF.CM.1, NF.CM.2

\textbf{Procedure}:
\begin{enumerate}[noitemsep]
    \item Place the PMB, base station, and Wi-Fi router at vertices of an equilateral triangle with side length of 30 meters.
    \item Establish a streaming video connection.
    \item Check the streaming quality on the base station.
\end{enumerate}

\textbf{Verification}: 
To pass, the connection must be stable (no obvious lost frames may be noticed at the base station).