\paragraph{\underline{T.FS.1: Full System Flight Test}}

This test verifies the flight capability of the fully integrated system.

\textbf{Addresses}: F.HL.1

\textbf{Procedure}:
\begin{enumerate}[noitemsep]
    \item Turn on the computing platform, ensuring the PMB and PLB are secured on the RPAS.
    \item Using the RPAS controller, direct the RPAS to rise from its ground position to a comfortable flight height.
    \item Using the RPAS controller, direct the RPAS to move horizontally in a wide range of directions.
    \item Using the RPAS controller, direct the RPAS to land back on the ground.
\end{enumerate}

\textbf{Verification}:
Confirm that the RPAS, mounted with the PMB and PLB, is capable of lifting off, flying in all directions and landing safely down on the ground.

%

\paragraph{\underline{T.FS.2: Full System ML Processing Test}}

This test verifies the ML processing capability of the fully integrated system.

\textbf{Addresses}: F.HL.2, F.HL.3, F.HL.4

\textbf{Procedure}:
\begin{enumerate}[noitemsep]
    \item Turn on the computing platform, ensuring the PMB and PLB are secured on the RPAS.
    \item Using the RPAS controller, direct to RPAS to rise from its ground position to a comfortable flight height.
    \item Check the base station interface to ensure there is real-time video and ML data being displayed.
\end{enumerate}

\textbf{Verification}:
Confirm that the fully integrated system is capable of ML processing, from taking in captured video on the PMB to displaying accurate ML data and captured video on the base station.