\documentclass[10pt,letterpaper]{article}
\input{../common/include}

% Custom definitions
\newcommand{\doctitle}{Validation Specification}
\newcommand{\docsubtitle}{\input{../common/title}}

\input{../common/aliases}
\input{../common/urlsetup}
\input{../common/pagesetup}
\input{../common/titlepage}

% Begin Document
\begin{document}

\input{../common/presections}



% TODO: fill out all the sections
% if the sections gets too long, move them to a separte .tex document
\section{About This Document}

\subsection{Purpose}
This document serves to outline the methods, tests, and scenarios which are used to validate the project, and the status of these validation steps. In addition, this document outlines the validation methodology, which describes how the validation steps themselves are written and performed.

\subsection{Intended Audience}
This document is intended for:
\begin{itemize}
\item \textbf{Quality Controllers (the Capstone team)}: to assess the validation methodology and results,
\item \textbf{Designers (the Capstone team)}: to assess the current degree of completion of the project,
\item \textbf{Client (and their representatives)}: to assess the final state of the project (when complete),
\item \textbf{and Legal Personnel:} to review the validation scheme if necessary. Such personnel may include individuals from the Department of Electrical and Computer Engineering, Industry Canada, and Transport Canada.
\end{itemize}

This document is particularly relevant to those who wish to assess the current state of the project, in addition to those who will assess the validation methodology against academic, organizational, or legal criteria.

\subsection{Reading Guide}
This document begins with a description of the validation methodology, describing differing types of tests and how they are identified. The description of tests begins in Section \ref{begintest}, with each test case listing the requirements being tested, the steps taken to execute the test, and the test's success parameters. Finally, the current status of each test is summarized in Section \ref{results}. Any pertinent test results are additionally included as appendices, as appropriate.

The requirements referenced in this document can be found in the \textit{Requirements Specification}.

\section{Validation Overview}

\subsection{Test Organization}\label{auto}
The validation tests employed are split into two categories: \textit{automated tests} and \textit{manual tests}:

\textbf{Automated tests} are tests focused on tasks which are performed regularly by the device and \textit{can be monitored by the device itself}. Examples of such tests include self-tests on boot, self-monitoring of communication status, machine learning accuracy logging, et cetera.

\textbf{Manual tests} are tests which \textit{cannot be performed by the device itself} and must be manually performed by a quality controller. These tests are performed less frequently --- some may be executed before every flight, while others may only be performed once. 

\subsection{Test Notation}
The following notations and conventions are used throughout this document:

\textbf{Verification Requirement (VR)}: The unique identifier of a specific test. These identifiers always start with \textbf{T}.

\textbf{Design Requirement (DR)}: Denotes the design requirement which the test is exercising, as listed in the project's \textit{Requirements Specification}. Requirement identifiers are encoded by their first characters, as follows:
\begin{itemize}
	\item \textbf{F}: Functional Requirement,
	\item \textbf{NF}: Non-Functional Requirement, and
	\item \textbf{C}: Constraint
\end{itemize}

\textbf{Status}: The status of a specific test:
\begin{itemize}
	\item \textbf{PEND} if the specific test has never been performed,
	\item \textbf{FAIL} if the specific test is currently failing, or
	\item \textbf{PASS} if the specific test is currently passing
\end{itemize}

\textbf{Effective Date}: Denotes the date at which the test was last performed (and thus, when the status was last updated). This field is not applicable for pending tests.

\textbf{It is important to note that a one-to-one mapping of VRs to DRs \textit{does not necessarily exist}}. Some requirements (particularly those which are high-level or functional) will have no tests, while some requirements will have multiple tests. It is also possible for one test to exercise multiple design requirements at once.

\section{Automated Test Cases} \label{begintest}

%\subsection{Computing Platform Tests}
\input{3_1_automated_computing_platformtest.tex}

%\subsection{Multirotor Tests}
%\input{3_2_automated_multirotor_test.tex}

\section{Manual Test Cases}

\subsection{Computing Platform Tests}
\subsubsection{General Tests}
\input{4_1_1_general_test.tex}

\subsubsection{Camera Tests}
\input{4_1_2_camera_test.tex}

\subsubsection{Machine Learning Tests}
\input{4_1_3_machine_learning_test.tex}

\subsubsection{Base Station Tests}
\input{4_1_4_base_station_tests.tex}

\subsubsection{Power Tests}
\input{4_1_5_power_test.tex}

\subsection{Multirotor Tests}
\input{4_2_multirotor_tests.tex}

\subsection{Full System Tests}
\input{4_3_full_system_tests.tex}

\section{Verification Results} \label{results}

\subsection{Automated Verification Results}
\begin{table}[H]
	\centering
	\begin{tabular}{lllll}
	\hline
	\textbf{VR} & \textbf{DR} & \textbf{Status} & \textbf{Eff. Date} & \textbf{Note}\\
	\hline
	T.ACP.1 & F.CM.1, F.CM.2, F.BS.3, F.BS.5 & PEND   & \\
	T.ACP.2 & NF.CP.1, F.ML.1, F.ML.2, F.ML.4 & PEND   & \\
	\hline
	\end{tabular}
\end{table}

\subsection{Manual Verification Results}
\subsubsection{Computing Platform Verification Results}
\begin{table}[H]
	\centering
	\begin{tabular}{lllll}
	\hline
	\textbf{VR} & \textbf{DR} & \textbf{Status} & \textbf{Eff. Date} & \textbf{Note}\\
	\hline
	T.G.1 & F.CP.2 & PEND   & \\
	T.G.2 & F.CP.4, F.BS.5 & PEND   & \\
	T.G.3 & F.BS.3, NF.CM.1, NF.CM.2 & PEND   & \\
	\hline
	T.CM.1 & NF.CAM.3, NF.CAM.4   & PEND   & \\
	T.CM.2 & NF.CAM.1, NF.CAM.2   & PEND   & \\
	T.CM.3 & F.CAM.2, NF.CAM.6   & PEND   & \\
	T.CM.4 & NF.CAM.5   & PEND   & \\
	\hline
	T.ML.1 & F.ML.1, F.ML.4 & PASS & 3-FEB-20 & See Appendix \ref{appendix:T.ML.1}.\\
	T.ML.2 & F.HL.2, F.ML.1, F.ML.4 & FAIL  & 5-FEB-20 & FPS is currently \textasciitilde 0.33, need to optimize data flow. \\
    T.ML.3 & F.ML.3 & PEND   & \\
    \hline
    T.BS.1 & F.CM.1, F.CP.1 & PEND   & \\
    \hline
    T.P.1 & NF.PR.1 & PASS   & 1-FEB-20 & See Appendix \ref{appendix:T.P.1}.\\
    T.P.2 & F.PR.4, F.PR.5, F.PR.6 & PEND   & \\
	\hline
	\end{tabular}
\end{table}

\subsubsection{Multirotor Verification Results}
\begin{table}[H]
	\centering
	\begin{tabular}{lllll}
	\hline
	\textbf{VR} & \textbf{DR} & \textbf{Status} & \textbf{Eff. Date} & \textbf{Note}\\
	\hline
    T.DR.1 & NF.DR.1, NF.DR.12, NF.DR.13  & PEND   & \\
	T.DR.2 & NF.DR.7, NF.DR.10 & PEND   & \\
	\hline
	\end{tabular}
\end{table}

\subsubsection{Full System Verification Results}
\begin{table}[H]
	\centering
	\begin{tabular}{lllll}
	\hline
	\textbf{VR} & \textbf{DR} & \textbf{Status} & \textbf{Eff. Date} & \textbf{Note}\\
	\hline
    T.FS.1 & F.HL.1  & PEND   & \\
	T.FS.2 & F.HL.2, F.HL.3, F.HL.4 & PEND   & \\
	\hline
	\end{tabular}
\end{table}



% Bibliography
\clearpage
\addcontentsline{toc}{section}{References}
\bibliographystyle{ieeetr}
\bibliography{references}

% Appendix (uncomment to enable appendix)
 \clearpage
 \appendix
 \section*{Appendices}
 \section{Sample Image Test (\textit{T.ML.1}) Results}\label{appendix:T.ML.1}
 \section{Power Usage Test (\textit{T.P.1}) Results}\label{appendix:T.P.1}

% Content here

\end{document}